\documentclass[11pt]{article}
\usepackage{fullpage,times,url}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
{\Large {\bf Biographical Sketch for Amr Sabry}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Preparation}

\begin{itemize}
\item Cairo University, Egypt, Electronics \& Computer Engineering, B.Sc.
  (1986)
\item Cairo University, Egypt, Computer Engineering, M.Sc. (1989)
\item Rice University, Computer Science, M.Sc. (1993) 
\item Rice University, Computer Science, Ph.D. (1994) 
\item Chalmers University, Sweden, Programming Languages, Postdoctoral
  researcher (1994-1995)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appointments}

\begin{itemize}
\item{2007-Present} Professor, School of Informatics and Computing,
Indiana University.
\item{2000-2007} Associate Professor, Computer Science Department,
Indiana University.
\item{Spring 2004} Visiting Professor, Genova University, Italy.
\item{Fall 2003} Visiting Researcher, Microsoft Research, Cambridge, UK.
\item{1995-2000} Assistant Professor, Department of Computer and
Information Science, University of Oregon.
\item{1994-1995} Postdoctoral Researcher, Department of Computer Science,
  Chalmers University, G\"oteborg, Sweden.
\item{1993-1994} Research Assistant, Rice University, visiting Carnegie 
Mellon University.
\item{1989-1993} Research and Teaching Assistant, Rice University.
\item{1987} Teaching Assistant, Polytechnic Military School, Egypt. 
\item{1986-1989} Research and Teaching Assistant, Cairo University, Egypt.
\item{1986-1989} Programmer and Consultant, Pacer, Egypt.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Closely Related Publications} 

\begin{enumerate}

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung
  Tai. ``Discrete Quantum Theories.'' In \emph{J. Phys. A: Math. Theor.},
  \textbf{47}, 2014. 

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung Tai,
  ``Geometry of Discrete Quantum Computing.'' In \emph{J. Phys. A:
  Math. Theor.}, \textbf{46}, 2013. 

\item Juliana K. Vizzotto, Andr\'e Rauber Du Bois, and Amr Sabry, ``The Arrow
  Calculus as a Quantum Programming Language,'' In the \emph{Workshop on Logic,
  Language, Information and Computation}, 2009.

\item Thorsten Altenkirch, Jonathan Grattage, Juliana K. Vizzotto, and Amr
  Sabry, ``An Algebra of Pure Quantum Programming.'' In the \emph{Workshop on
  Quantum Programming Languages}, 2005. Final version in the \emph{Electronic
  Notes in Theoretical Computer Science}, vol. 170, pp. 23-47, 2007.

\item Juliana K. Vizzotto, Thorsten Altenkirch, and Amr Sabry, ``Structuring
  Quantum Effects: Superoperators as Arrows.''  \emph{Mathematical Structures
    in Computer Science} (MSCS), Volume 16, Issue 03, pages 453-468, June
  2006.

\end{enumerate} 

\section*{Other Significant Publications} 

\begin{enumerate}

\item Jacques Carette and Amr Sabry, ``Computing with Semirings and Weak Rig
  Groupoids.'' In the \emph{European Symposium on Programming}, ESOP 2016.

\item Roshan P. James and Amr Sabry, ``Information Effects.'' In the
  \emph{Conference Record of the ACM Symposium on Principles of Programming
  Languages}, 2012.

\item Amr Sabry, ``Side Effects.'' In \emph{Wiley Encyclopedia of Computer
  Science and Engineering, 5-Volume Set}, Volume 4, pages 2534-2543, Benjamin
  W. Wah (Editor), Hoboken: John Wiley \& Sons, Inc, January 2009.

\item Eugenio Moggi and Amr Sabry: Monadic encapsulation of effects: 
a revised approach (extended version). \emph{J. Funct. Program.} 11(6):
591-627 (2001)

\item Cormac Flanagan, Amr Sabry, Bruce F. Duba, and Matthias Felleisen:
The Essence of Compiling with Continuations. In the Proceedings of the ACM
SIGPLAN Conference on Programming Language Design and Implementation, pages
237-247, 1993. \emph{Selected as one of the best 50 PLDI papers from
1979-1999.}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Synergetic Activities}

Paul Purdom and Amr Sabry, CNF Generator for Factoring Problems.  Software
system to generate satisfiability problems used in the SAT competition
organized in conjunction with the Sixth International Conference on the
Theory and Applications of Satisfiability Testing, March 2003, and
continually used by designers of SAT solvers worldwide. Available online at
\url{http://www.cs.indiana.edu/cgi-pub/sabry/cnf.html}.

\end{document}