\documentclass[11pt]{article}
\usepackage{fullpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Data Management Plan}
\author{}
\date{}
\maketitle


The research conducted as part of this project will produce the following
deliverables:
\begin{itemize}
\item research papers and technical reports,
\item software libraries and models, and
\item curriculum materials for undergraduate students, graduate students, and
summer school participants.
\end{itemize}

\paragraph*{Research papers and technical reports.}
All papers and publications that appear in pertinent journals and
conferences will be made available through the websites of the principal
investigators and the arXiv. The websites are regularly backed up as part of
the Indiana University computational infrastructure.  

\paragraph*{Software libraries and models.}
Polished libraries will be developed using robust software engineering
approaches with high coding and documentation standards. We will use an
external code repository and make the software, documentation, and examples
available under an open source license. All experimental artifacts will be
archived by the principal investigators and made freely available upon
request to interested researchers.  

\paragraph*{Curriculum materials.}
We anticipate developing lecture notes and other teaching materials and we
will make every effort to make these publicly available to students and other
teachers as appropriate.

\end{document}
